Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-08 writeup/conStruct.tex
convert multipanel figs for submission

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[authoryear]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bigints}
\usepackage{array}
\usepackage{tikz}
\usepackage{longtable}
\usepackage{geometry}

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_pies:nsp_K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_pies:nsp_K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_pies:nsp_K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K4.pdf}}
		\subcaptionbox{$K=2$\label{simK1_pies:sp_K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K5.pdf}}
		\subcaptionbox{$K=3$\label{simK1_pies:sp_K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K6.pdf}}
		\subcaptionbox{$K=4$\label{simK1_pies:sp_K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using the nonspatial model for $K=2$ through 4 (top row)
	and also the spatial model for $K=2$ through 4 (bottom row).
	The data were simulated using a single cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_pies}
\end{figure}

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{populus_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp2.pdf}}
		\subcaptionbox{$K=3$\label{populus_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp3.pdf}}
		\subcaptionbox{$K=4$\label{populus_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp4.pdf}}
	\caption{
	Map of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 4.
    }\label{populus_pies}
\end{figure}

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=3$ (spatial)\label{bear_K3:sp}}
			{\includegraphics[width=2.5in,height=2.5in]{figs/bears/bear_sp3.pdf}}
		\subcaptionbox{$K=3$ (nonspatial)\label{bear_K3:nsp}}
			{\includegraphics[width=2.5in,height=2.5in]{figs/bears/bear_nsp3.pdf}}
	\caption{
	Maps of admixture proportions estimated for the black bear dataset 
	using the spatial model (left) and the nonspatial model (right) for $K=3$.
	Pies show mean admixture results across individuals within their diameter, 
	and the admixture results for all individuals included within each group are 
	shown in the plot above.
    }\label{bear_K3}
\end{figure}

@@

Results from the nonspatial model clearly exhibit the tendency 
of nonspatial clustering algorithms to describe continuous spatial patterns of divergence 
using gradients of admixture between clusters.
For example, in Fig \ref{bear_K3:nsp}, 
the third cluster (in green) exhibits a clear East-West gradient that 
is overlain across the discrete structure between the Southwest cluster and the Southeast

Across all values of $K$ for which we ran \texttt{conStruct},
we see strong support for the spatial model over the nonspatial model (Fig \ref{bear_xvals}),
indicating the isolation by distance seems to be a prominent feature of the data.
This pattern may resolve a discrepancy between our results and 
previous analyses that split Alaskan and British Columbian bears out 
into their own cluster with an inferred Beringian glacial refugium
\citep{Byun1997,Stone2000,Puckett2015}.
Our model, which explicitly incorporates a spatial decay of relatedness, 
allows somewhat genetically differentiated individuals 
that are sampled far from one another to belong to the same layer,
instead of splitting these individuals out into successive clusters 
(e.g., Fig \ref{bear_sp_pies:K5} vs \ref{bear_nsp_pies:K5}).

@@

A second caveat is that, in some instances, 
membership in the same cluster may not mean that samples are particularly related.
If covariance within a cluster decays sharply with distance, 
and the cluster-specific relatedness parameter $\phi^{(k)}$ is low, 
individuals at a far spatial remove may be in the same cluster but have very low pairwise relatedness.
It is possible that this is happening in Fig \ref{populus_sp_pies}\subref{populus_sp_pies:K3}. 
At $K=3$, the southernmost populations of \textit{P. trichocarpa} are in the yellow cluster, 
whose other neighbors are to the north, with an intervening group of populations in the red cluster, 
and at $K=5$, those southernmost samples split out and become their own cluster.
Again, we encourage users to run analyses across multiple values of $K$, 
and to examine the spatial covariance functions within layers when interpreting results.

@@

\newpage
\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK1_nsp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK1_nsp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK1_nsp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using a single cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK1_sp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK1_sp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK1_sp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using 1 cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}

@@

\newpage
\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK2_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_nsp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK2_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_nsp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK2_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_nsp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK2_nsp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_nsp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK2_nsp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_nsp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK2_nsp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_nsp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using two clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK2_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK2_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_sp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK2_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_sp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK2_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_sp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK2_sp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_sp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK2_sp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_sp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK2_sp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK2_sp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using two clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK2_sp_pies}
\end{figure}

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK3_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_nsp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK3_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_nsp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK3_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_nsp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK3_nsp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_nsp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK3_nsp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_nsp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK3_nsp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_nsp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using three clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK3_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK3_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_sp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK3_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_sp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK3_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_sp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK3_sp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_sp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK3_sp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_sp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK3_sp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK3_sp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using three clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK3_sp_pies}
\end{figure}
\clearpage

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{populus_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp2.pdf}}
		\subcaptionbox{$K=3$\label{populus_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp3.pdf}}
		\subcaptionbox{$K=4$\label{populus_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp4.pdf}}
		\subcaptionbox{$K=5$\label{populus_sp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp5.pdf}}
		\subcaptionbox{$K=6$\label{populus_sp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp6.pdf}}
		\subcaptionbox{$K=7$\label{populus_sp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_sp7.pdf}}
	\caption{
	Map of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 7.
    }\label{populus_sp_pies}
\end{figure}

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{populus_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_nsp2.pdf}}
		\subcaptionbox{$K=3$\label{populus_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_nsp3.pdf}}
		\subcaptionbox{$K=4$\label{populus_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_nsp4.pdf}}
		\subcaptionbox{$K=5$\label{populus_nsp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_nsp5.pdf}}
		\subcaptionbox{$K=6$\label{populus_nsp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_nsp6.pdf}}
		\subcaptionbox{$K=7$\label{populus_nsp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/populus/populus_nsp7.pdf}}
	\caption{
	Map of admixture proportions estimated for the \textit{Populus} dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{populus_nsp_pies}
\end{figure}

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{bear_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_sp2.pdf}}
		\subcaptionbox{$K=3$\label{bear_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_sp3.pdf}}
		\subcaptionbox{$K=4$\label{bear_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_sp4.pdf}}
		\subcaptionbox{$K=5$\label{bear_sp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_sp5.pdf}}
		\subcaptionbox{$K=6$\label{bear_sp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_sp6.pdf}}
		\subcaptionbox{$K=7$\label{bear_sp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_sp7.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the spatial model for $K=2$ through 7.
    }\label{bear_sp_pies}
\end{figure}

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{bear_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_nsp2.pdf}}
		\subcaptionbox{$K=3$\label{bear_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_nsp3.pdf}}
		\subcaptionbox{$K=4$\label{bear_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_nsp4.pdf}}
		\subcaptionbox{$K=5$\label{bear_nsp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_nsp5.pdf}}
		\subcaptionbox{$K=6$\label{bear_nsp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_nsp6.pdf}}
		\subcaptionbox{$K=7$\label{bear_nsp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/bears/bear_nsp7.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{bear_nsp_pies}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[authoryear]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bigints}
\usepackage{array}
\usepackage{tikz}
\usepackage{longtable}
\usepackage{geometry}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/Fig2_simK1_sp_vs_nsp.pdf}}
	\caption{
	Map of admixture proportions estimated using the nonspatial model for $K=2$ through 4 (top row)
	and also the spatial model for $K=2$ through 4 (bottom row).
	The data were simulated using a single cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_pies}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=2in]{figs/populus/Fig4_pop_sp_results.pdf}}
	\caption{
	Map of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 4.
    }\label{populus_pies}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=3in]{figs/bears/Fig6_sp_vs_nsp.pdf}}
	\caption{
	Maps of admixture proportions estimated for the black bear dataset 
	using the spatial model (left) and the nonspatial model (right) for $K=3$.
	Pies show mean admixture results across individuals within their diameter, 
	and the admixture results for all individuals included within each group are 
	shown in the plot above.
    }\label{bear_K3}
\end{figure}

@@

Results from the nonspatial model clearly exhibit the tendency 
of nonspatial clustering algorithms to describe continuous spatial patterns of divergence 
using gradients of admixture between clusters.
For example, in Fig \ref{bear_K3}b, 
the third cluster (in green) exhibits a clear East-West gradient that 
is overlain across the discrete structure between the Southwest cluster and the Southeast

Across all values of $K$ for which we ran \texttt{conStruct},
we see strong support for the spatial model over the nonspatial model (Fig \ref{bear_xvals}),
indicating the isolation by distance seems to be a prominent feature of the data.
This pattern may resolve a discrepancy between our results and 
previous analyses that split Alaskan and British Columbian bears out 
into their own cluster with an inferred Beringian glacial refugium
\citep{Byun1997,Stone2000,Puckett2015}.
Our model, which explicitly incorporates a spatial decay of relatedness, 
allows somewhat genetically differentiated individuals 
that are sampled far from one another to belong to the same layer,
instead of splitting these individuals out into successive clusters 
(e.g., Fig \ref{bear_sp_pies}d vs \ref{bear_nsp_pies}d).

@@

A second caveat is that, in some instances, 
membership in the same cluster may not mean that samples are particularly related.
If covariance within a cluster decays sharply with distance, 
and the cluster-specific relatedness parameter $\phi^{(k)}$ is low, 
individuals at a far spatial remove may be in the same cluster but have very low pairwise relatedness.
It is possible that this is happening in Fig \ref{populus_sp_pies}. 
At $K=3$, the southernmost populations of \textit{P. trichocarpa} are in the gold cluster, 
whose other neighbors are to the north, with an intervening group of populations in the red cluster, 
and at $K=5$, those southernmost samples split out and become their own cluster.
Again, we encourage users to run analyses across multiple values of $K$, 
and to examine the spatial covariance functions within layers when interpreting results.

@@

\newpage
\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK1_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using a single cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK1_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using 1 cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}

@@

\newpage
\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK2_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using two clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK2_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK2_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using two clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK2_sp_pies}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK3_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using three clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK3_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK3_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using three clusters with nearest-neighbor symmetric migration between demes.
    }\label{simK3_sp_pies}
\end{figure}
\clearpage

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 7.
    }\label{populus_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated for the \textit{Populus} dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{populus_nsp_pies}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/bears/bear_sp_results.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the spatial model for $K=2$ through 7.
    }\label{bear_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/bears/bear_nsp_results.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{bear_nsp_pies}
\end{figure}
